final_project_draft

### 2022-04-06 draft.Rmd
April 6th graded before class commit. Worked more with theme() and changed a few things.

ggplot(data = high_donations, aes(x = amount, y = owner_ordered, label = Recipient, colour = party)) +
  geom_point() +
  labs(x = " ", 
       y = " ",
       title = "Top 25 Highest Political Donations by NFL Team Owners in 2016",
       colour = "Political Party",
       subtitle = "What Influence Could NFL Team Owners Have on Elections?") +
  scale_colour_viridis_d() +
  theme_bw()
```

@@

ggplot(data = frequent, aes(x = amount, y = Owner, label = Amount, colour = Party)) +
  geom_point() +
  labs(title = "How Much Do They Donate?",
       y = "Owners",
       x = "Amount Donated",
       colour = "Party") +
  scale_colour_brewer(palette = "Dark2") +
  theme(legend.position = "bottom")

@@

ggplot(data = cj_party, aes(x = party, y = n, fill = Party)) +
  geom_col() +
  coord_flip() +
  scale_fill_viridis_d() +
  labs(title = "Count of Donations by Political Party?",
       x = "Political Party",
       y = "Count") +
  theme(legend.position = "bottom") +
  geom_label(data = cj_party, aes(label = n), show.legend = FALSE) 
```

@@

kable(organizations, caption = "What Are Some Organizations Charles Johnson Donates To?",
      col.names = c("Recipient", "Political Party", "Amount of Donations Made"))  %>%
  kable_classic()
```

@@

ggplot(data = recipients, aes(x = recipient, y = n, colour = Party)) +
  geom_point() +
  geom_segment(aes(x = recipient, xend = recipient, y = 0, yend = n)) +
  coord_flip() +
  labs(x = "Recipients",
       y = "Count") +
  labs(title = "Organizations Receiving Most Donations Across All Leagues") +
  theme_bw() +
  scale_colour_brewer(palette = "Dark2") +
  theme(legend.position = "bottom")
```

@@

plot6 <- ggplot(data = blockbusters1, aes(x = release_year, y = imdb_rating, colour = mpaa_rating,
                                          label = Film)) +
  geom_point() +
  labs(y = "IMDB Rating",
       x = "Release Year",
       colour = "MPAA Rating",
       title = "Blockbuster Ratings: 1977 to 2019") +
  theme_hc() +
  scale_colour_brewer(palette = "Dark2")

ggplotly(plot6, tooltip = "label")
```

## Has the Budget for Blockbusters Increased Throughout Time? 
```{r}
ggplot(data = blockbusters, aes(x = release_year, y = film_budget, colour = release_year)) +
  geom_point() +
  geom_smooth(se = FALSE, method = "lm") +
  labs(x = "Release Year",
       y = "Film Budget",
       title = "Has the Budget for Blockbusters Increased Throughout Time?",
       subtitle = "Film Budget for Blockbuesters: 1977-2019") +
  theme_bw() +
  scale_colour_viridis_c() +
  theme(legend.position = "none")

ggplot(data = blockbusters, aes(x = release_year, y = film_budget)) +
  geom_hex() +
  geom_smooth(se = FALSE, method = "lm") +
  labs(x = "Release Year",
       y = "Film Budget", 
       title = "Has the Budget for Blockbusters Increased Throughout Time?",
       subtitle = "Film Budget for Blockbuesters: 1977-2019") +
  theme_bw() 
```

@@

ggplot(data = blockbusters3, aes(x = order, y = n, fill = order)) +
  geom_col() +
  coord_flip() +
  geom_label(data = blockbusters3, aes(label = n), show.legend = FALSE) +
  labs(x = "Amount of Films Produced",
       y = "Domestic Distributor",
       title = "Amount of Blockbusters Produced by Domestic Distributors: 1977-2019") +
  theme_bw() +
  theme(legend.position = "none")
```

## Work in Progress 
```{r}
blockbusters

interest <- blockbusters %>% mutate(rank = rank(desc(imdb_rating))) %>%
  select(rank, everything()) %>%
  arrange(rank) %>%
  slice(1:5) %>%
  mutate(film_title = fct_recode(film_title, 
                                 LOTR_The_Return_Of_The_King = "The Lord of the Rings: The Return of the King",
                                 LOTR_Fellowship_Of_The_Ring = "The Lord of the Rings: The Fellowship of the Ring"))
interest

@@

library(ggrepel)
ggplot(data = interest, aes(x = release_year, y = domestic_gross)) +
  geom_point() +
  geom_label_repel(data = interest, aes(label = film_title)) +
  geom_point(data = interest2, aes(x = release_year, y = domestic_gross)) +
  geom_label_repel(data = interest2, aes(label = film_title))
```

>>>>

ggplot(data = high_donations, aes(x = amount, y = owner_ordered, label = Recipient, colour = party)) +
  geom_point(size = 3) +
  labs(x = " ", 
       y = " ",
       title = "How Much Did NFL Owners Donate in 2016?",
       colour = "Political Party",
       subtitle = "What Influence Could NFL Team Owners Have on Elections?") +
  scale_colour_viridis_d() +
  theme_bw() +
  theme(plot.title = element_text(family = "mono",
                                  face = "bold",
                                  size = 15,
                                  margin = margin(c(t = 20,
                                                    b = 50,
                                                    vjust = 10))),
        plot.subtitle = element_text(family = "mono",
                                     face = "italic",
                                     size = 10),
        legend.title = element_text(family = "mono",
                                    face = "bold",
                                    size = 8),
        legend.text = element_text(family = "mono",
                                   size = 8),
        axis.text = element_text(family = "mono",
                                 size = 8),
        legend.box.background = element_rect(),
        legend.position = "bottom")
```

@@

ggplot(data = frequent, aes(x = amount, y = Owner, label = Amount, colour = Party)) +
  geom_point() +
  labs(title = "How Many Donations Have They Made?",
       subtitle = "Examining The Monetary Amount of Observed Political Donations",
       y = " ",
       x = " ",
       colour = "Party") +
  scale_colour_brewer(palette = "Dark2") +
    theme_bw() +
  theme(legend.position = "bottom",
        plot.title = element_text(family = "mono",
                                  face = "bold",
                                  size = 12,
                                  margin = margin(c(t = 50,
                                                    b = 50)),
                                  vjust = 10),
        axis.text.x = element_text(family = "mono"),
        axis.text.y = element_text(family = "mono"),
        legend.title = element_text(family = "mono", 
                                    face = "bold",
                                    size = 7),
        legend.text = element_text(family = "mono",
                                   size = 6),
        plot.subtitle = element_text(family = "mono",
                                     face = "italic",
                                     size = 9,
                                     vjust = 5),
        legend.box.just = "left",
        legend.box.background = element_rect())

@@

ggplot(data = cj_party, aes(x = party, y = n, fill = Party)) +
  geom_col() +
  coord_flip() +
  scale_fill_viridis_d() +
  labs(title = "Is There Any Political Party Receiving More Support From Charles Johnson?",
       x = " ",
       y = "Count of Donations") +
  theme(legend.position = "bottom",
        plot.title = element_text(family = "mono",
                                  face = "bold",
                                  hjust = 0.5,
                                  size = 13,
                                  margin = margin(c(t = 50,
                                                    b = 50)),
                                  vjust = 10),
        axis.text = element_text(family = "mono"),
        legend.title = element_text(family = "mono",
                                    face = "bold"),
        legend.text = element_text(family = "mono"),
        axis.ticks.y = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.x = element_text(family = "mono",
                                    size = 9,
                                    face = "italic",
                                    margin = margin(t = 20))) +
  geom_label(data = cj_party, aes(label = n), show.legend = FALSE,
             label.size = 1)
```

@@

kable(organizations, caption = "<b>What Are Some Organizations Charles Johnson Donates To?<b>",
      col.names = c("Recipient", "Political Party", "Amount of Donations Made"))  %>%
  kable_styling(html_font = "Cambria", bootstrap_options = "striped",
                font_size = 15) %>%
  scroll_box(height = "500px")
```

@@

new_names <- c("Collins For Senator", "McSally for Senate Inc.",
               "ActBlue", "Portman For Senate Committee", "NRCC",
               "NRSC", "Hillary Victory Fund", "Team Ryan", 
               "Office of the Commissioner of MLB PAC", "Gridirion PAC")

ggplot(data = recipients, aes(x = recipient, y = n, colour = Party)) +
  geom_point() +
  geom_segment(aes(x = recipient, xend = recipient, y = 0, yend = n)) +
  coord_flip() +
  labs(x = " ",
       y = "Count of Donations") +
  labs(title = "Organizations Receiving Most Donations Across All Leagues") +
  scale_colour_brewer(palette = "Dark2") +
  theme(legend.position = "bottom") +
  scale_x_discrete(labels = new_names) +
  theme(plot.title = element_text(family = "mono",
                                  face = "bold",
                                  margin = margin(c(t = 50,
                                                    b = 50)),
                                  vjust = 10),
        axis.text = element_text(family = "mono"),
        axis.title = element_text(family = "mono",
                                  size = 8),
        axis.title.x = element_text(size = 10,
                                    margin = margin(t = 20,
                                                    b = 10)),
        legend.title = element_text(family = "mono",
                                    face = "bold"),
        legend.text = element_text(family = "mono"),
        axis.ticks = element_blank(),
         legend.box.background = element_rect())
```

@@

plot6

ggplot(data = blockbusters1, aes(x = release_year, y = imdb_rating, colour = mpaa_rating,
                                          label = Film)) +
  geom_point() +
  facet_wrap(~mpaa_rating) +
  geom_smooth(se = FALSE, method = 'lm') +
  labs(y = "IMDB Rating",
       x = "Release Year",
       colour = "MPAA Rating",
       title = "Blockbuster Ratings: 1977 to 2019") +
  theme_hc() +
  scale_colour_brewer(palette = "Dark2") +
  theme(plot.title = element_text(family = "mono",
                                  face = "italic",
                                  margin = margin(t = 20, b = 20)),
        axis.ticks = element_blank(),
        axis.title = element_text(family = "mono",
                                  face = "italic"),
        axis.text = element_text(family = "mono"),
        legend.box.background = element_rect(),
        legend.text = element_text(family = "mono"),
        legend.title = element_text(family = "mono",
                                    face = "italic"),
        axis.title.y = element_text(margin = margin(r = 20)),
        axis.title.x = element_text(margin = margin(t = 20, b = 10)),
        strip.text = element_text(family = "mono",
                                  face = "bold"))
```

## Has the Budget for Blockbusters Increased Throughout Time? 
```{r}
ggplot(data = blockbusters, aes(x = release_year, y = film_budget, colour = release_year)) +
  geom_point() +
  geom_smooth(se = FALSE, method = "lm", colour = "black") +
  labs(x = "Release Year",
       y = "Film Budget",
       title = "Has the Budget for Blockbuster Films Increased Throughout Time?",
       subtitle = "Film Budget for Blockbusters: 1977-2019") +
  theme_bw() +
  scale_colour_viridis_c() +
  theme(legend.position = "none",
        plot.title = element_text(family = "mono",
                                  face = "bold",
                                  margin = margin(c(t = 50, b = 50)),
                                  vjust = 10),
        plot.subtitle = element_text(family = "mono",
                                     face = "italic",
                                     vjust = 5),
        axis.title = element_text(family = "mono",
                                  face = "bold"),
        axis.text = element_text(family = "mono"),
        axis.ticks = element_blank(),
        axis.title.x = element_text(margin = margin(c(l = 20))),
        axis.title.y = element_text(margin = margin(c(t = 20, b = 20, r = 20)))) 
## need to add more to this visualization 
```

@@

ggplot(data = blockbusters3, aes(x = order, y = n, fill = order)) +
  geom_point() +
  geom_segment(aes(x = order, xend = order, y = 0, yend = n)) +
  coord_flip() +
  geom_label(data = blockbusters3, aes(label = n), show.legend = FALSE) +
  labs(x = "Amount of Films Produced",
       y = "Domestic Distributor",
       title = "Amount of Blockbusters Produced by Domestic Distributors: 1977-2019") +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(family = "mono",
                                  face = "bold",
                                  margin = margin(c(t = 50)),
                                  vjust = 10),
        axis.title = element_text(family = "mono",
                                  face = "bold"),
        axis.text = element_text(family = "mono"),
        axis.text.y = element_text(face = "italic"),
        axis.ticks = element_blank(),
        axis.title.x = element_text(margin = margin(c(b = 20))),
        axis.title.y = element_text(margin = margin(c(t = 30, r = 30))))
```

## Work in Progress 
```{r}
blockbusters
interest <- blockbusters %>% mutate(rank = rank(desc(imdb_rating))) %>%
  select(rank, everything()) %>%
  arrange(rank) %>%
  slice(1:5) %>%
  mutate(film_title = fct_recode(film_title, 
                                 LOTR_The_Return_Of_The_King = "The Lord of the Rings: The Return of the King",
                                 LOTR_Fellowship_Of_The_Ring = "The Lord of the Rings: The Fellowship of the Ring"))
interest

@@

library(ggrepel)
ggplot(data = interest, aes(x = release_year, y = domestic_gross)) +
  geom_point(aes(colour = imdb_rating)) +
  geom_label_repel(data = interest, aes(label = film_title)) +
  geom_point(data = interest2, aes(x = release_year, y = domestic_gross, colour = imdb_rating)) +
  geom_label_repel(data = interest2, aes(label = film_title))
```
